---
title: "Coffee Rating "
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
tt_load("2020-07-07")

CoffeBean <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv')

view(CoffeBean)
colnames(CoffeBean)
```

```{r}
## Block code 2 
## Let create a dataset on which we can sum all coffee attributes and compare this sum ## to the total cup point. 
  
Attributes<-CoffeBean %>% 
  mutate(
    grand_total_check = select(
      ., aroma:cupper_points
    ) %>% rowSums(na.rm = T)
  ) 
view(Attributes)
```


```{r}
## Block code 3 Beginning of Data Manipulation 

## We start Exploratory Data Analysis with generate a dataset with only the 
## attributes

OnlyAttributes<- Attributes %>% 
  select(aroma:cupper_points)

View(OnlyAttributes)
```


```{r}
## check for any missing value

is.na(OnlyAttributes$aroma)
is.na(OnlyAttributes$flavor)
is.na(OnlyAttributes$aftertaste)
is.na(OnlyAttributes$acidity)
is.na(OnlyAttributes$body)
is.na(OnlyAttributes$balance)
is.na(OnlyAttributes$uniformity)
is.na(OnlyAttributes$clean_cup)
is.na(OnlyAttributes$sweetness)
is.na(OnlyAttributes$cupper_points)
```

```{r}
## Block code 4
## Ranking per Attributes
## Determine the list countries with more the 10 samples

WithAtList10Samples<- CoffeBean %>% 
  group_by(country_of_origin) %>% 
  count() %>% 
  filter(n>10)

view(WithAtList10Samples)
```
```{r}
CoffeBeanWith10Countries<-CoffeBean %>% 
  filter(country_of_origin %in% c("Brazil","China","Colombia","Costa Rica","El Salvador","Ethiopia","Guatemala","Honduras","India","Indonesia","Kenya","Malawi","Mexico","Nicaragua","Taiwan","Thailand","Tanzania, United Republic Of","Uganda","United States(Hawaii)"))
view(CoffeBeanWith10Countries)
```

```{r}
MedianAroma <- CoffeBeanWith10Countries %>% 
  group_by(country_of_origin) %>% 
  summarise(RankAroma=median(aroma))
view(MedianAroma)
```

```{r}
MedianFlavor <- CoffeBeanWith10Countries %>% 
  group_by(country_of_origin) %>% 
  summarise(RankFlavor=median(flavor))
view(MedianFlavor)
```


```{r}
MedianAFterTaste <- CoffeBeanWith10Countries %>% 
  group_by(country_of_origin) %>% 
  summarise(RankAftertaste=median(aftertaste))
view(MedianAFterTaste)
max(MedianAFterTaste$RankAftertaste)
```

```{r}
## Acidity 
MedianAcidity <- CoffeBeanWith10Countries %>% 
  group_by(country_of_origin) %>% 
  summarise(RankAcidity=median(acidity))
view(MedianAcidity)
```
```{r}
## Body

MedianBody <- CoffeBeanWith10Countries %>% 
  group_by(country_of_origin) %>% 
  summarise(RankBody=median(body))
view(MedianBody)
```
```{r}
## Balance

MedianBalance <- CoffeBeanWith10Countries %>% 
  group_by(country_of_origin) %>% 
  summarise(RankBalance=median(balance))
view(MedianBalance)
```

```{r}
## Uniformity

MedianUniformity  <- CoffeBeanWith10Countries %>% 
  group_by(country_of_origin) %>% 
  summarise(RankAftertaste=median(uniformity))
view(MedianUniformity)
```

```{r}
## Clean Cup

MedianClean_cup <- CoffeBeanWith10Countries %>% 
  group_by(country_of_origin) %>% 
  summarise(RankClean_cup=median(clean_cup))
view(MedianClean_cup)
```

```{r}
## Sweetness
MedianSweetness <- CoffeBeanWith10Countries %>% 
  group_by(country_of_origin) %>% 
  summarise(RankSweetness=median(sweetness))
view(MedianSweetness)
```

```{r}
## Cupper Points

MedianCupperPoint <- CoffeBeanWith10Countries %>% 
  group_by(country_of_origin) %>% 
  summarise(RankCupperpoints=median(cupper_points))
view(MedianCupperPoint)
```


```{r}

```


## Including Plots

You can also embed plots, for example:

```{r}
ggplot(CoffeBean , aes(x=country_of_origin))+
  geom_bar()
```


```{r}

radarchart(BrazilData,
           seg=10,
           title= "Brazil Radar Plot",
           pfcol=scales::alpha("gray",0.3),
           plwd = 2)
```



```{r}
radarchart(EthiopiaData,
           seg=10,
           title= "Ethiopia Radar Plot",
           pfcol=scales::alpha("gray",0.3),
           plwd = 2)
```

```{r}
ggplot(MedianCupperPointPerYear2, aes(x=harvest_year,y=RankCupperpoints))+
  geom_col()+
  coord_cartesian(ylim=c(70,90))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
